\bf Calendar-based graphics for visualizing people's daily schedules

### 2019-05-08 main.Rmd
minor tweak

The `frame_calendar()` function described in Section \@ref(sec:algorithm) is a data restructuring function rather than a plotting tool. Thus, a full pipeline inevitably involves two separate steps: data transforming and data plotting. We provide an alternative method `facet_calendar()` that extends the **ggplot2** graphical system so that to be able to make a calendar plot with one shot. A faceting method lays out panels in a grid. The faceting calendar method simply requires a variable containing dates for preparing a sequence of panels defined by Equation \@ref(eq:grid), and the coordinates and everything else have been taken care by **ggplot2** internals.

>>>>

The `frame_calendar()` function described in Section \@ref(sec:algorithm) is a data restructuring function rather than a plotting tool. Thus, a full pipeline inevitably involves two separate steps: data transforming and data plotting. We provide an alternative method `facet_calendar()` that extends the **ggplot2** graphical system so that to be able to make a calendar plot with a one-off procedure. A faceting method lays out panels in a grid. The faceting calendar method simply requires a variable containing dates for preparing a sequence of panels defined by Equation \@ref(eq:grid), and the coordinates and everything else have been taken care by **ggplot2** internals.

### 2019-05-08 main.tex
minor tweak

The \texttt{frame\_calendar()} function described in Section \ref{sec:algorithm} is a data restructuring function rather than a plotting tool. Thus, a full pipeline inevitably involves two separate steps: data transforming and data plotting. We provide an alternative method \texttt{facet\_calendar()} that extends the \textbf{ggplot2} graphical system so that to be able to make a calendar plot with one shot. A faceting method lays out panels in a grid. The faceting calendar method simply requires a variable containing dates for preparing a sequence of panels defined by Equation \eqref{eq:grid}, and the coordinates and everything else have been taken care by \textbf{ggplot2} internals.

>>>>

The \texttt{frame\_calendar()} function described in Section \ref{sec:algorithm} is a data restructuring function rather than a plotting tool. Thus, a full pipeline inevitably involves two separate steps: data transforming and data plotting. We provide an alternative method \texttt{facet\_calendar()} that extends the \textbf{ggplot2} graphical system so that to be able to make a calendar plot with a one-off procedure. A faceting method lays out panels in a grid. The faceting calendar method simply requires a variable containing dates for preparing a sequence of panels defined by Equation \eqref{eq:grid}, and the coordinates and everything else have been taken care by \textbf{ggplot2} internals.
